---
title: "Lab 2"
author: "Leah, Tess, Maheeka"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
Question set 1:
1. What is the overall number of chocolate bars rated? There are 1,852 chocolate bars being rated in this data set. 

```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 

#The most ratings occured in 2015. The data is left skewwed, with most of the rating occuring between 2016 and 2018.

```{r}
library(ggplot2)
library(tidyverse)
ggplot(choco, aes(x = Review.Date)) + geom_bar(aes(weight= Review.Date)) 
```
Question set 2:
For each of the questions below provide at least one graphic as a basis for your answer.
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
##Description: The histogram seems to be slighlty left skewed with a few outliers on either side. It looks like most chocolates are rated in the range of 2.5 to 4. Very few were rated 1 or 5.

```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram()
```

2, Do ratings depend on the cocoa percentage of a chocolate bar?
#Description: There is no clear trend or relation between ratings and Cocoa Percentage.

```{r}
ggplot(data = choco, aes(x = Rating, y=Cocoa.Pct)) + geom_point()
```


3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
Upload your answers to the repository. Discuss and refine answers as a team.

#description: USA has the most number of highly rated chocolate followed by France and Canada.


```{r}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

```

```{r}
ggplot(top3, aes(x = Rating)) + geom_histogram() + facet_wrap(.~ Company.Location)
```
Leah Question: How does Location effect rating? 

#Answer: There doesn't seem to be a relationship between Company location and rating. Italy does have an outlier of a rating of 5. 

```{r}
ggplot(data = choco, aes(x = Company.Location, y = Rating)) + geom_point() + coord_flip()
```
Maheeka Question: What is the trend of rating in Germany based on Broad Bean origin? What is the origin of the bean that has highest ratings in Germany?
#Hence Beans originating from Venezuala have highest ratings in Germany followed by Madagascar.

```{r }
Germany <- dplyr::filter(choco, Company.Location %in% c("Germany"))
ggplot(data = Germany, aes(x = Rating)) + facet_wrap(~Broad.Bean.Origin, scale = "free_y") + geom_histogram()
```
#Tess:
Does bean origin affect rating?
```{r}
ggplot(choco, aes(x = Broad.Bean.Origin, y = Rating)) + geom_point(aes(color = Rating)) +coord_flip() + facet_wrap(~Broad.Bean.Origin)
```
There are multiple origin countries with many beans originating from there. It is easy to 
see that when there are multiple beans originating from one country, there is a gradient from rating 1 to rating 5. When there is only one dot, we see there wasn't many beans originating from there. There is not enough data, and it would be interesting to look into this further- looking at origin countries with >5 originating beans, then making a final decision.  



##Workflow
We met after class one day and decided Leah would start the repository and share it with the rest of the group. We decided to all do the homework on our own, then meet up to discuss if we got the same answers, or if we needed to have discussions about how we did things differently. We ended up having similar responses to the questions, with some minor changes on a couple of questions. These questions involved the same response, just a slightly varying way of doing it. This was great, because we were able to learn from each other and see new ways of doing things! Maheeka and Tess pushed their RMarkdown files to the lab 2 repository so Leah could submit the homework and then we can all have the final draft. 

