---
title: "Lab 2"
author: "Leah, Tess, Maheeka"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
Question set 1:
1. What is the overall number of chocolate bars rated? There are 1,852 chocolate bars being rated in this data set. 

```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 

#The most ratings occured in 2015. The data is left skewwed, with most of the rating occuring between 2016 and 2018.

```{r}
library(ggplot2)
library(tidyverse)
ggplot(choco, aes(x = Review.Date)) + geom_bar(aes(weight= Review.Date)) 
```
Question set 2:
For each of the questions below provide at least one graphic as a basis for your answer.
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
##Description: The histogram seems to be slighlty left skewed with a few outliers on either side. It looks like most chocolates are rated in the range of 2.5 to 4. Very few were rated 1 or 5.

```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram()
```

2, Do ratings depend on the cocoa percentage of a chocolate bar?
#Description: There is no clear trend or relation between ratings and Cocoa Percentage.

```{r}
ggplot(data = choco, aes(x = Rating, y=Cocoa.Pct)) + geom_point()
```


3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
Upload your answers to the repository. Discuss and refine answers as a team.

#description: USA has the most number of highly rated chocolate followed by France and Canada.


```{r}
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

```

```{r}
ggplot(top3, aes(x = Rating)) + geom_histogram() + facet_wrap(.~ Company.Location)
```
Leah Question: How does Location effect rating? 

#Answer: There doesn't seem to be a relationship between Company location and rating. Italy does have an outlier of a rating of 5. 

```{r}
ggplot(data = choco, aes(x = Company.Location, y = Rating)) + geom_point() + coord_flip()
```
Maheeka Question: What is the trend of rating in Germany based on Broad Bean origin? What is the origin of the bean that has highest ratings in Germany?
#Hence Beans originating from Venezuala have highest ratings in Germany followed by Madagascar.

```{r }
Germany <- dplyr::filter(choco, Company.Location %in% c("Germany"))
ggplot(data = Germany, aes(x = Rating)) + facet_wrap(~Broad.Bean.Origin, scale = "free_y") + geom_histogram()
```


