---
title: "Lab 2"
author: "Leah, Tess, Maheeka"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
Question set 1:
1. What is the overall number of chocolate bars rated? There are 1,852 chocolate bars being rated in this data set. 

```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 
The most ratings occured in 2015. The data is left skewwed, with most of the rating occuring between 2016 and 2018.

```{r}
library(ggplot2)
library(tidyverse)
ggplot(choco, aes(x = Review.Date)) + geom_bar(aes(weight= Review.Date)) 
```
Question set 2:
For each of the questions below provide at least one graphic as a basis for your answer.
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
2, Do ratings depend on the cocoa percentage of a chocolate bar?
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
Upload your answers to the repository. Discuss and refine answers as a team.
