---
title: "Maheeka_Lab2"
output: html_document
date: "2023-03-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

#Question set 2: part 1

```{r }
library(ggplot2)
ggplot(data = choco, aes(x = Rating)) + geom_histogram()
```
#Description: The histogram seems to be slighlty left skewed with a few outliers on either side. It looks like most chocolates are rated in the range of 2.5 to 4. Very few were rated 1 or 5.

#Question set 2: part 2

```{r }
ggplot(data = choco, aes(x = Rating, y = Cocoa.Pct)) + geom_point()
```
#Description: There is no clear trend or relation between ratings and Cocoa Percentage.

#Question set 2: part 3
```{r }
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

ggplot(data = top3, aes(x = Rating, y = Cocoa.Pct)) + facet_wrap(~Company.Location, scale = "free_y") + geom_point()
```
```{r }
ggplot(data = top3, aes(x = Rating)) + facet_wrap(~Company.Location, scale = "free_y") + geom_histogram()
```
#description: USA has the most number of highly rated chocolate followed by France and Canada.

#My own Question: What is the trend of rating in Germany based on Broad Bean origin? What is the origin of the bean that has highest ratings in Germany?

```{r }
Germany <- dplyr::filter(choco, Company.Location %in% c("Germany"))

ggplot(data = Germany, aes(x = Rating)) + facet_wrap(~Broad.Bean.Origin, scale = "free_y") + geom_histogram()
```
#Hence Beans originating from Venezuala have highest ratings in Germany followed by Madagascar.
